Diversity dynamics in Nymphalidae butterflies: Effect of phylogenetic uncertainty on diversification rate shift estimates

### 2014-12-19 response_to_reviewers.tex

Page 5, Estimation of trait-dependent... section, replace “can be feeding on” with “are able to feed on members of”

\textbf{11. Response:}

\begin{quote}
\color{blue}
We made the suggested corrections.
\end{quote}

\textbf{12. Reviewer's Comment:}
 Page 5, Detecting diversification shifts... section: should final number be 1.884, instead of 1,884?

\textbf{12. Response:}

\begin{quote}
\color{blue}
We have removed the whole sentence as the reviewer recommended in point 5.
\end{quote}

\textbf{13. Reviewer's Comment:}
Page 6, sentence beginning “For the diversification shifts..”: the last phrase could use a verb; something like “when the MCC tree alone was used”.

\textbf{13. Response:}

\begin{quote}
\color{blue}
We added "was used" to the end of the sentence.
\end{quote}
\end{document}

### 2014-12-19 MS_revised.tex
comment 13

For the diversification shifts found in both the MCC tree and most of
the samples of 1000 trees (frequency more than 90\%; Table 2), the
MultiMEDUSA approach recovered different rates of diversification than
those found when the MCC tree alone.

>>>>

For the diversification shifts found in both the MCC tree and most of
the samples of 1000 trees (frequency more than 90\%; Table 2), the
MultiMEDUSA approach recovered different rates of diversification than
those found when the MCC tree alone was used.
